\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-04-04 popl-2019-journal-v/paper.tex
[POPLjv] Describe unsealing

  In the example, if we use sealing, we can seal the return capability which does two things.
  It prevents the untrusted code from changing the target of the return capability forcing them to return to the point we intended.
  It also prevents the untrusted code from reading our capabilities.
  All in all, this means that we can transfer control to another domain without giving up our capabilities or handing them over.
\end{jversion}

>>>>

  In the example, if we use sealing, we can seal the return capability which does two things.
  It prevents the untrusted code from changing the target of the return capability forcing them to return to the point we intended.
  It also prevents the untrusted code from reading our capabilities.
  All in all, this means that we can transfer control to another domain without giving up our capabilities or handing them over.

  \trgcm{} does not have a direct unsealing instruction, but it is still possible to do some amount of unsealing.
  Say you have a sealed non-executable word $\sealed{\sigma,w}$ as well as a set of seals $\seal{\sigma_\baddr,\sigma_\eaddr, \sigma}$ that contains the $\sigma$, i.e.\ $\sigma \in [\sigma_\baddr,\sigma_\eaddr]$.
  Now assume part of the code would like to have access to $w$ in $\rdata$.
  Take a capability for this code, possibly by adjusting the pc, and seal it with $\sigma$.
  Now you have the data part and the code part of a sealed capability pair, so you can $\txjmp{}{}$ to it which unseals the data capability and puts it in $\rdata$ for your code to use.
  Sealed executable capabilities cannot be unsealed in the same way because $\txjmp{}{}$ fails if the data capability is executable.
  However, given a sealed executable capability $\sealed{\sigma,c}$ and a set of seals that contains $\sigma$, we can still construct the data part of the sealed capability pair.
  This means that we can execute the code the capability points to in the presence of any data we can construct.

  Sealing is meant for encapsulation, but it gives us very weak encapsulation properties if seals are not private as the unsealing example illustrates.
  For this reason, it is important that the system is setup, so each component has access to seals that are unique to that component.
  We return to this in \sectionname~\ref{sec:well-form-reas}.
\end{jversion}
